The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-21 analysis/paper/paper.qmd
Update geocode function
Add function to convert data frame to document term matrix

```{r}
# The topicmodels package requires a document-term matrix as input
emu_theses_dtm <- emu_theses_words |> 
  count(title, word, sort = TRUE) |> 
  cast_dtm(title, word, n)

emu_theses_dtm

>>>>

```{r}
# The {topicmodels} package requires a document-term matrix as input
emu_theses_dtm <- convert_to_dtm(emu_theses_words, "title", "word")
emu_theses_dtm
